---
title: "OUCRU_data"
author: "01NVb-Thaontp"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, echo=FALSE}
rm(list = ls(all.names = TRUE))
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.cap = " ", size = "tiny")
```

```{r}

library(readxl)
library(readr)
library(tidyverse)
library(gtsummary)
library(table1)
library(writexl)
library(labelled)
library(rio)
library(psych)
library(kableExtra)
library(lattice)
library(plotly)
library(gsubfn)
library(gt)
library(car)
library(lme4)
library(sjPlot)
library(Amelia)
library(ggpubr)
library(ROCR)
library(pROC)
library(rcompanion)
library(pacman)
library(nlme)
library(Hmisc)
library(ggeffects)
library(data.table)
library(vcd)
library(Amelia)
fulldata <- import_list("C:/Thaontp/Thao/Muscle/DataFeb2023.xlsx")

list2env(fulldata, .GlobalEnv)

##Tetanus

tetanus <- TETANUS

cns <- CNS

demograph <- ADM %>% 
	filter(USUBJID %in% c(tetanus$USUBJID, cns$USUBJID))

dischargedate <- DIS %>% select(USUBJID, OUTCOME, ICUDISDTC, DAYSOFICU)

demograph <- left_join(demograph, dischargedate, by = "USUBJID") %>%
	relocate(ICUDTC, .before = ICUDISDTC) %>% 
	filter(USUBJID %in% MUSCLE_MuscleUls$USUBJID) %>%
	mutate(Stayicu = as.numeric(ICUDISDTC - ICUDTC + 1)) %>% 
	mutate_at(c("ICUDTC", "ICUDISDTC"), ~as.Date(.))

demograph <- demograph %>% select(USUBJID, OUTCOME, Stayicu, HYPERTENSION:ELECTIVESURGERY,IMMUNOCOMPROMISED)

admission <- ADM %>% select(USUBJID, ADMDTC)

##missing AGE in SCR

SCR1 <- left_join(SCR, admission, by = "USUBJID") %>% 
	mutate(ADMDTC = as.numeric(format(ADMDTC, "%Y"))) %>% 
	mutate(AGE = ifelse(is.na(AGE) == TRUE, as.numeric(ADMDTC - YEAROFBIRTH), AGE))

add_demo <- select(SCR1, USUBJID, AGE, SEX) %>% 
	filter(USUBJID %in% c(tetanus$USUBJID, cns$USUBJID))

demograph <- left_join(demograph, add_demo,  by = "USUBJID") %>%
	mutate(SEX = ifelse(SEX == "F", "Female", "Male"))

##Filter patients in MUSCLE RF-CSA

##Select muscle data have at least 1 measure

demograph <- demograph %>% mutate(group = case_when(USUBJID %in% tetanus$USUBJID ~ "Tetanus",
																										USUBJID %in% cns$USUBJID ~ "CNS"))

#Pick date of admission to get full AGE

stringreplace <- function(x){
	if_else(x == "Y", 1L, 0L, as.integer(NA))
}

demograph <- demograph %>%
  mutate(across(c(HYPERTENSION:IMMUNOCOMPROMISED), na_if, "UNKNOWN"))

demograph <- demograph %>% 
	mutate(across(c(HYPERTENSION:IMMUNOCOMPROMISED), stringreplace))

demograph <- demograph %>% 
	filter(!USUBJID %in% c("003-212")) ##Exclude Food poisoning patient

#demograph <- demograph[demograph$USUBJID %in% quolchange$USUBJID,]

```
Muscle admission size bias by AGE, WEIGHT and SEX with significant p-value

```{r muscle standardize with physical values}

muscle <- MUSCLE_MuscleUls %>% 
	filter(if_any(c(N1, N2, N3), ~ !is.na(.))) %>% 
	filter(USUBJID %in% demograph$USUBJID)

##for those are missing

muscle <- muscle %>% 
	rowwise() %>% 
	mutate(AVERAGE = round(mean(c(N1, N2, N3), na.rm = TRUE), 2)) %>% 
	filter(AVERAGE != 0)

##Admission muscle

muscleadmission <- muscle %>% 
	select(USUBJID, MUSCLE_SEQ, MUSCLE_MuscleUls_SEQ, AVERAGE, XSECTIONAREA) %>%
	filter(MUSCLE_SEQ == 1) %>% 
	left_join(ADM, by = "USUBJID") %>% 
	left_join(demograph, by = "USUBJID") %>% 
	select(USUBJID, AGE, XSECTIONAREA, AVERAGE, WEIGHT, HEIGHT, SEX, group) %>% 
	mutate(BMI = round(WEIGHT/(HEIGHT/100)^2, 2))

##Test the normality of Muscle

#qqPlot(muscleadmission$AVERAGE)

#missmap(muscleadmission, main = "Missing observed")

##Every patient will have 2 value of muscle at admission (Right and left leg)

geomadmission <- muscleadmission %>% 
	group_by(USUBJID) %>% 
	mutate(ad_muscle = round(geometric.mean(c(AVERAGE[XSECTIONAREA == "RLeg"], AVERAGE[XSECTIONAREA == "LLeg"])), 3)) %>% 
	select(-c(XSECTIONAREA, AVERAGE)) %>% 
	unique()

#pairs(data = geomadmission,
#    ~ ad_muscle + WEIGHT + HEIGHT + AGE + BMI)


muscle_age <- glm(formula = ad_muscle ~ AGE + WEIGHT + SEX, data = geomadmission)

muscle_age1 <- glm(formula = AVERAGE ~ AGE + WEIGHT + SEX, data = geomadmission)

#corr.test(geomadmission[,-c(1)],
#          use    = "pairwise",
#          method = "pearson",
#          adjust = "none")

#summary(muscle_age)

tab_model(muscle_age)

tab_model(muscle_age1)
##plot random effect of all considered parameters
#plot_model(muscle_con, type = "diag")

#plot_model(muscle_age, type = "diag")

compareGLM(muscle_age, muscle_age1)

##To exclude the multicollinearity from the later model, we should choose the less coorelation independent variables to be predictors, which will escape the influence amongst them.

##when VIF or tolerance is equal to 1, the ith independent variable is not correlated to the remaining ones, meaning that multicollinearity does not exist. VIF between 1 and 5 = variables are moderately correlated. VIF greater than 5 = variables are highly correlated

```
####Edited version

After consideration, I choose Geometric mean which is appropriated for situation involving change of subjects are not independent of each other. Geometric mean = nth root of product of n subject, example 3 subjects have geometric mean equal cube root of a*b*c | Explain: n is number of subjects, a, b, c... are values of each subject

As we can see in comparison 2 models, the first one based on Geometric mean shows lowe AIC and BIC which indicates it is better than the second one.
```{r muscle analyse}

change_muscle <- muscle %>% 
	select(USUBJID, MUSCLE_SEQ, XSECTIONAREA, AVERAGE) %>% 
	pivot_wider(names_from = XSECTIONAREA, values_from = AVERAGE)

change_muscle <- change_muscle %>% 
	arrange(USUBJID, MUSCLE_SEQ) %>% 
	group_by(USUBJID)

##For missing data of one of 2 legs, find the linear regression between 2 legs then use the equation to predict the missed one

ggplot(change_muscle, aes(RLeg, LLeg)) +
  geom_point() +
  stat_smooth(method = lm)

legs <- lm(RLeg ~ LLeg, data = change_muscle)

tab_model(legs)

summary(legs)$sigma

summary(legs)

```
The equation for linear relationship between Right leg and left leg

$\displaystyle RLeg = 0.32062 + $ $0.98421 \times LLeg$ $ + 0.8344652$ ($\varepsilon = 0.8344652$ is the error or variance of the model)

$\displaystyle LLeg = \frac{RLeg- 0.32062 - 0.8344652}{0.98421}$

We use this equation to predict missed values.

```{r}
##Add-in missing rows

change_muscle <- change_muscle %>% 
	ungroup() %>% 
	rowwise() %>% 
	mutate(RLeg = replace_na(RLeg, round(as.numeric(0.32062 + 0.98421*LLeg + 0.8344652), 2)),
				 LLeg = replace_na(LLeg, round(as.numeric((RLeg - 0.32062 - 0.8344652)/0.98421), 2)))

##Each leg muscle size is converted to ratio of the last muscle measurement to the first, so if 0 < rate < 1 the muscle area has decrease, if rate > 1 the muscle has increase, if rate = 1 the muscle is the same. Calculate geometric mean between rateRleg and rateLleg before create the model.

##Length of ICU stay

icustay <- demograph %>% 
	select(USUBJID, Stayicu)

##Choose time 3 and time 1 to calculate muscle loss per day (divided by LOS in ICU)

change_muscle_day <- change_muscle %>% 
	filter(!MUSCLE_SEQ == 4) %>%
	group_by(USUBJID) %>% 
	group_by(USUBJID, MUSCLE_SEQ) %>% 
	mutate(meangeom = geometric.mean(c(RLeg, LLeg)))

change_muscle_day <- change_muscle_day %>% 
	select(USUBJID, MUSCLE_SEQ, meangeom) %>% 
	pivot_wider(names_from = MUSCLE_SEQ, values_from = meangeom)

change_muscle_day <- change_muscle_day %>% 
	group_by(USUBJID) %>% 
	mutate(stage1 = round((`1` - `2`)/`1`, 3),
				 stage2 = round((`2` - `3`)/`2`, 3),
				 admission_discharge = round((`1` - `3`)/`1`, 3)) %>% 
	left_join(icustay, by = "USUBJID")

change_muscle_day <- change_muscle_day %>% 
	mutate(perday = ifelse(!is.na(admission_discharge), round(admission_discharge/Stayicu, 3), NA)) %>% 
	filter(if_any(c(stage1:admission_discharge), ~ !is.na(.)))

change_muscle_day <- change_muscle_day %>% 
	mutate_at(c("stage1", "stage2", "admission_discharge", "perday"), ~as.numeric(100*.))

change_muscle_day <- change_muscle_day %>% 
	mutate(staygroup = case_when(Stayicu <= 10 ~ "10 days",
															 Stayicu > 10 & Stayicu <= 20 ~ "11-20 days",
															 Stayicu > 20 & Stayicu <= 30 ~ "21-30 days",
															 TRUE ~ "More than 30 days"))

change_muscle_day %>% 
	ungroup() %>% 
	select(stage1:staygroup) %>% 
	tbl_summary(by = staygroup, missing = "no", label = list(stage1 ~ "MW during first 7 days", stage2 ~ "MW during later ICU period", admission_discharge ~ "Total MW in ICU", Stayicu ~ "ICU length of stay", perday ~ "Total MW per day")) %>% 
	as_gt() %>%
  gt::tab_source_note(gt::md("*MW: Muscle wasting measured by percentage*"))

```
Look at the first and second rows, MW happens the most dramatic in days 21-30, patients with the higher rate of MW at first 7 days can have 2 possible outcomes: ICU stay shorter than 10 days or higher than 30 days. In the MW per day (which is equal to total MW divided by LOS in ICU) could have been inverse linear with increasing in LOS but it gets its highest peek at period 21-30, so we can see the MW occurs significantly during this time and stop happening after that or the patients start to gain muscle back.

Muscle change are no longer belong to AGE, SEX and WEIGHT. The model show that: in admission the size of muscle are distributed in the context of other's effect, but the muscle loss don't dependent on physical factors, so we should turn to clinical factors or efficacy of treatment. 

Model of trending in muscle loss with Subject ID is a random effect (because we want to see the change between time points, the Individual and their intrinsic physiology are assumed to be just random factor).
```{r}

##Pick up the Dead outcome after discharge from SF36
deadafter <- SF36 %>% select(USUBJID, Note)

timeonset_te <- tetanus %>% select(USUBJID, FIRSTSYMTOHOSPPERIOD)

timeonset_cns <- cns %>% 
	select(USUBJID, DAYSOFSYMPTOM) %>% 
	rename(FIRSTSYMTOHOSPPERIOD = DAYSOFSYMPTOM)

##Combine all data from Tetanus and CNS

timeonset <- rbind(timeonset_te, timeonset_cns) %>% 
	filter(USUBJID %in% demograph$USUBJID) %>% 
	left_join(deadafter, by = "USUBJID") %>%
	left_join(demograph, by = "USUBJID") %>%
	select(USUBJID, FIRSTSYMTOHOSPPERIOD, Stayicu, Note) %>% 
	left_join(DIS, by = "USUBJID") %>% 
	select(USUBJID, Stayicu, FIRSTSYMTOHOSPPERIOD, OUTCOME, Note, DAYSOFMECHVENT) %>%
	group_by(USUBJID) %>% 
	group_modify(~.x %>% mutate(Note = ifelse(str_detect(Note, "Discharge for end of life care|Dead") == TRUE, "Death", NA))) %>% 
	unique() %>% 
	mutate(newoutcome = if_else(if_any(c("OUTCOME", "Note"), ~. %in% c("TransferToDie", "Death")) == TRUE, "Death", "Alive")) %>% ##New outcome during follow up
	filter(row_number() == n()) %>% 
	filter(USUBJID %in% demograph$USUBJID)

#admission_muscle <- select(muscleadmission, USUBJID, AVERAGE)

#timeonset <- timeonset %>%
	#select(-changeLleg) %>% 
	#rename(changesum = changeRleg) %>% 
#	mutate(newoutcome = factor(newoutcome, level = c("Alive", "Death")),
#				 SEX = factor(SEX, level = c("Male", "Female")))

timeonset <- timeonset %>% replace_na(list(
	FIRSTSYMTOHOSPPERIOD = round(mean(timeonset$FIRSTSYMTOHOSPPERIOD, na.rm = TRUE), 0)))

##Join newoutcome to demograph

newoutcome <- timeonset %>% select(USUBJID, newoutcome)
library(ggeffects)

```

```{r, eval = FALSE}
##Sequence

model1 <- lmer(AVERAGE ~ MUSCLE_SEQ + (MUSCLE_SEQ|USUBJID), data = muscle)

ggpredict(model1, terms = c('MUSCLE_SEQ')) %>% plot()

model_outcome <- left_join(muscle, newoutcome, by = "USUBJID")

model_outcome$newoutcome <- factor(model_outcome$newoutcome, levels = c("Alive", "Death"))

model2 = lme(AVERAGE ~ MUSCLE_SEQ + newoutcome, random = ~1|USUBJID,
            data=model_outcome,
            method="REML")


ggpredict(model2, terms = c("MUSCLE_SEQ", "newoutcome")) %>% plot()

#model.fixed = gls(AVERAGE ~ MUSCLE_SEQ,
#                  data=muscle,
#                  method="REML")

#ggeffects::ggeffect(model.fixed, terms = c('MUSCLE_SEQ')) %>% 
#  plot()


#predict1 <- ggeffects::ggpredict(model1)

#plot(predict1)

#beta <- coef(model1)$USUBJID

#beta1 <- beta$`(Intercept)`
#beta2 <- beta$MUSCLE_SEQ

#df <- as.data.frame(beta)
#df <- rownames_to_column(df, "USUBJID")

#timeonset <- left_join(timeonset, df, by = "USUBJID")

#timeonset <- timeonset %>% rename(Beta1 = `(Intercept)`,
#																	Beta2 = MUSCLE_SEQ)

#fit <- glm(newoutcome ~ Beta1 + Beta2, data = timeonset, family = binomial)


```


```{r relation to onset period}

demograph <- left_join(demograph, newoutcome, by = "USUBJID")

demo <- demograph %>% 
	select(-c(USUBJID, OUTCOME, ANGINA, CONGESTIVEGRADE13, ANAEMIA, CONGESTIVEGRADE4, HEMIPLEGIA, PERIPHERAL, DEMENTIA, SEVERE, ANYMALIGNANCY)) %>%
	tbl_summary(by = newoutcome, label = c(AGE ~ "Age - years, Median(IQR)",
												SEX ~ "Sex, n(%)",
												Stayicu ~ "ICU length of stay, Median (IQR)",
												HYPERTENSION ~ "Hypertension, n(%)",
												MYOCARDIAL ~ "Myocardiac disease, n(%)",
												CEREBROVASCULAR ~ "Cerebrovascular disease, n(%)",
												CHRONIC ~ "Chronic pulmonary disease, n(%)",
												CONNECTIVE ~ "Connective tissue disease, n(%)",
												PEPTICULCER ~ "Peptic ulcer disease, n(%)",
												MILDLIVER ~ "Mild liver disease, n(%)",
												MODERATELIVER ~ "Moderate/severe liver disease, n(%)",
												MODERATEKIDNEY ~ "Moderate/severe kidney disease, n(%)",
												DIABETES ~ "Diabetes, n(%)",
												DIABETESCHRONIC ~ "Diabetes with chronic complications, n(%)",
												METASTATIC ~ "Metastatic solid tumour, n(%)",
												SMOKER ~ "Smoker, n(%)",
												ELECTIVESURGERY ~ "Elective surgery within 30 days, n(%)",
												IMMUNOCOMPROMISED ~ "Immunocompromised, n(%)",
												group ~ "Admission disorder, n(%)"),
							missing = "no") %>% 
	as_gt() %>% 
	gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(groups = everything())
  )

demo

```

```{r}
mtab <- change_muscle_day %>% 
	select(USUBJID, admission_discharge)

mtab <- timeonset %>% 
	left_join(mtab, by = "USUBJID") %>% 
	select(USUBJID, DAYSOFMECHVENT, admission_discharge) %>% 
	left_join(demograph, by = "USUBJID") %>% 
	left_join(HAI, by = "USUBJID")

mtab <- mtab %>% 
	mutate(newoutcome = ifelse(newoutcome == "Death", 1, 0),
				 SEX = ifelse(SEX == "Female", 1, 0),
				 YES = if_else(YES == "TRUE", 1, 0, 0))
```
The histogram of total muscle change likely to be normal distribution with p-value for Shapiro-Wilk test 0.1759 (we received the p-value > 0.05). So the missing value will be replaced by sample mean.

```{r}

mtab <- mtab %>% mutate(admission_discharge = replace_na(admission_discharge, mean(mtab$admission_discharge, na.rm = TRUE)))

rrmodel <- glm(newoutcome ~ YES + Stayicu + DAYSOFMECHVENT + admission_discharge, data = mtab, family = poisson())

tbl_regression(rrmodel, exponentiate = T, label = c(YES ~ "HAIs", DAYSOFMECHVENT ~ "Days of MV", Stayicu ~ "ICU length of stay (days)", admission_discharge ~ "Muscle wasting (%)")) %>% bold_labels()

```
The HAIs is not the cause to death outcome, which even has $\displaystyle IRR = \frac{HAIsDeath}{NonHAIsDeath}$ 0.26 meaning that patients with HAIs are less likely to be death. While longer days of MV can give higher risk to death outcome.

Patients with longer stay in ICU tend to have alive outcome. And muscle wasting can be an indicator for alive outcome.

One meta-analysis called "The rate and assessment of muscle wasting during critical illness: a systematic review and meta-analysis" concluded that ICU patient will loss 2% of skeletal muscle per day during the first week of ICU admission, so that should be a strong argument for the presence of muscle wasting in these patients.
```{r eval = FALSE}


#missmap(timeonset, main = "Missing values vs observed")

##Edit missing data by mean of all sample

##test normality
#ks.test(timeonset$geomean, "pnorm", mean=mean(timeonset$geomean, na.rm = TRUE), sd=sd(timeonset$geomean, na.rm = TRUE))

##Find which factor can be a predictor for outcome

##Add random effect (confounder) as WEIGHT and BMI

#raneff <- ADM %>% 
#	select(USUBJID, WEIGHT, HEIGHT) %>% 
#	unique()%>% 
#	mutate(BMI = round(WEIGHT/(HEIGHT/100)^2, 2)) ##There are some patients don't have admission muscle so when first calculate BMI we didn't include them, this will be calculated again

#timeonset <- timeonset %>% left_join(raneff, by = "USUBJID")  %>% select(-Note)

##add the difference of muscle after all (negative results are muscle loss, positive results are muscle gain)

#timeonset <- timeonset %>% mutate(musclewaste = as.numeric(geomean - 1))

#model_test <- glmer(newoutcome ~ geomean + DAYSOFMECHVENT + geomean*Stayicu + (1|BMI) + (1|AGE), data = timeonset, family = "binomial")

#tab_model(model_test)

##AUC plot

#predict_test <- predict(model_test, newdata=timeonset, type="response", allow.new.levels = TRUE)
#prediction_test <- prediction(predict_test, timeonset$newoutcome)

#prf_test <- performance(prediction_test, measure = "tpr", x.measure = "fpr")

#ROCplot <- plot(prf_test, colorize=TRUE, main=paste("ROC for Outcome Prediction AUC:", round(performance(prediction_test, measure = "auc")@y.values[[1]], 3)))


##New model

#modela <- glmer(newoutcome ~ DAYSOFMECHVENT + changeharmonic + (1|BMI) + FIRSTSYMTOHOSPPERIOD, data = timeonset, family = "binomial") ## The same result with binomial(link = logit)

#tab_model(modela)

#

#predict_table <- cbind(timeonset, Prob = round(100*predict(modela, type = "response", newdata = timeonset, allow.new.levels = TRUE), 2))

#test <- predict(modela, type = "response", newdata = data.frame(FIRSTSYMTOHOSPPERIOD = 1, DAYSOFMECHVENT = 26, Stayicu = 20, AGE = 65, SEX = "M", changesum = 0.8, WEIGHT = 85, BMI = 15), allow.new.levels = TRUE)

##test the deviance of each variable to the model

#anova(modela, test="Chisq")

##AUC plot

#predict_tb <- predict(modela, newdata=timeonset, type="response", allow.new.levels = TRUE)
#prediction <- prediction(predict_tb, timeonset$newoutcome)

#prf <- performance(prediction, measure = "tpr", x.measure = "fpr")

#ROCplot <- plot(prf, colorize=TRUE, main=paste("ROC for Outcome Prediction AUC:", round(performance(prediction, measure = "auc")@y.values[[1]], 3)))

##Try some plots to see the probability prediction in particular predictor 

#plot_model(modela, type = "eff", terms = "changesum")

#plot_model(modela, type = "eff", terms = "DAYSOFMECHVENT")

#ROCplot

# + DAYSOFMECHVENT + changeharmonic
```


```{r medicine doses}
medicineeff <- left_join(mtab, DIS) %>% 
	select(USUBJID:admission_discharge, Stayicu, YES, TOTALDOSEMIDAZOLAM:TOTALDOSEPIPER)

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

##Discharge

relation_glance <- rcorr(as.matrix(medicineeff[,-c(1,5)]))

flattenCorrMatrix(relation_glance$r, relation_glance$P) %>% filter(p <= 0.05)



```
Total muscle wasting inversely correlates with ICU LOS (They gained muscle back for later period in ICU??) and Diazepam doses.

```{r sf36}

##clean enough data for SF36
library(purrr)
library(combinat)

sf36 <- SF36 %>% 
	select(USUBJID, SUBJID, NOTE, QUESTIONAIRESTYPE, HEALTHSTATUS:EXCELLENT) %>% 
	unique() %>% 
	filter(NOTE != "test" | is.na(NOTE) == TRUE) %>% ##Exclude test account
	select(-c(SUBJID, NOTE)) %>% 
	filter(USUBJID %in% demograph$USUBJID) %>% 
	filter(if_any(c(HEALTHSTATUS:EXCELLENT), ~!is.na(.))) %>% 
	group_by(USUBJID) %>% 
	group_modify(~.x %>% mutate(QUESTIONAIRESTYPE = ifelse(row_number() == 1, "Discharge", "Follow Up"))) %>% ##Rename the false questionaire type
	ungroup()

##Rearrange column to get the exact order of 36 questions
sf36 <- reduce(
  .x = list(c('USUBJID','EXCELLENT'), c('QUESTIONAIRESTYPE', 'USUBJID')), 
  .f = ~ relocate(.x, .y[1], .after = .y[2]),
  .init = sf36
)

##Convert Yes No to 1 and 2, fix the question 32 to 5 levels

sf36 <- sf36 %>% 
	mutate_at(vars("HINDERSOCIALCOMMU"), ~str_replace(., "6", "5")) %>% 
	mutate_at(vars("REDUCEAMOUNTTIME", "LESSWORKDONE", "LIMITEDWORKORACTIVITY", "TROUBLEPERFORMINGTASKS", "REDUCETIMEDURATION", "LESSDONEASWANT", "LESSCAREFUL"), ~str_replace_all(., c("Y" = "1", "N" = "2")))


##Scoring

scoring <- function(sf36){

gr1 <- function(x){
  case_when(x == "1" ~ 100,
            x == "2" ~ 75,
            x == "3" ~ 50,
            x == "4" ~ 25,
            x == "5" ~ 0)
}

sf36[,c(1,2,20,22,34,36)] <- sapply(sf36[,c(1,2,20,22,34,36)], function(x) gr1(x))

gr2 <- function(x){
  case_when(x == "1" ~ 0,
            x == "2" ~ 50,
            x == "3" ~ 100)
}

sf36[,c(3,4,5,6,7,8,9,10,11,12)] <- sapply(sf36[,c(3,4,5,6,7,8,9,10,11,12)], function(x) gr2(x))

gr3 <- function(x){
  case_when(x == "1" ~ 0,
            x == "2" ~ 100)
}

sf36[,c(13,14,15,16,17,18,19)] <- sapply(sf36[,c(13,14,15,16,17,18,19)], function(x) gr3(x))

gr4 <- function(x){
  case_when(x == "1" ~ 100,
            x == "2" ~ 80,
            x == "3" ~ 60,
            x == "4" ~ 40,
            x == "5" ~ 20,
            x == "6" ~ 0)
}

sf36[,c(21,23,26,27,30)] <- sapply(sf36[,c(21,23,26,27,30)], function(x) gr4(x))

gr5 <- function(x){
  case_when(x == "1" ~ 0,
            x == "2" ~ 20,
            x == "3" ~ 40,
            x == "4" ~ 60,
            x == "5" ~ 80,
            x == "6" ~ 100)
}

sf36[,c(24,25,28,29,31)] <- sapply(sf36[,c(24,25,28,29,31)], function(x) gr5(x))

gr6 <- function(x){
  case_when(x == "1" ~ 0,
            x == "2" ~ 25,
            x == "3" ~ 50,
            x == "4" ~ 75,
            x == "5" ~ 100)
}

sf36[,c(32,33,35)] <- sapply(sf36[,c(32,33,35)], function(x) gr6(x))

##Take the Mean for the NA values

sf36 <- sf36 %>% 
	mutate(across(c(HEALTHSTATUS:EXCELLENT), ~replace_na(.,round(mean(., na.rm = TRUE), 0))))

sf36 <- sf36 %>% 
	rowwise() %>% 
	mutate(pf = mean(c_across(c(3,4,5,6,7,8,9,10,11,12))),
				 rh = mean(c_across(c(13,14,15,16))),
				 rp = mean(c_across(c(17, 18, 19))),
				 ef = mean(c_across(c(23, 27, 29, 31))),
				 eb = mean(c_across(c(24, 25, 26, 28, 30))),
				 sf = mean(c_across(c(20, 32))),
				 pa = mean(c_across(c(21, 22))),
				 gh = mean(c_across(c(1, 33, 34, 35, 36))))
}

sf36 <- scoring(sf36)

##ORA

ORA <- sf36 %>% mutate(PF_Z = round((pf - 84.52404)/22.89490, 5),
                       RP_Z = round((rh - 81.19907)/33.79729, 5),
                       VT_Z = round((ef - 61.05453)/20.86942, 5),
                       SF_Z = round((sf - 83.59753)/22.37642, 5),
                       RE_Z = round((eb - 81.29467)/33.02717, 5),
                       MH_Z = round((rp - 74.84212)/18.01189, 5),
                       BP_Z = round((pa - 75.49196)/23.55879, 5),
                       GH_Z = round((gh - 72.21316)/20.16964, 5))

ORA <- ORA %>% 
	select(USUBJID, QUESTIONAIRESTYPE, PF_Z:GH_Z) %>% 
	mutate(AGG_PHYS = round((PF_Z*0.42402) + (RP_Z*0.35119) + (BP_Z*0.31754) + (GH_Z*0.24954) + (VT_Z*0.02877) + (SF_Z*-0.00753) + (RE_Z*-0.19206) + (MH_Z*-0.22069), 2),
				 AGG_MENT = round((PF_Z*-0.22999) + (RP_Z*-0.12329) + (BP_Z*-0.09731) + (GH_Z*-0.01571) + (VT_Z*0.23534) + (SF_Z*0.26876) + (RE_Z*0.43407) + (MH_Z*0.48581), 2)) %>% 
	mutate(PCS = 50 + (AGG_PHYS*10),
				 MCS = 50 + (AGG_MENT*10))

##Describe improvement from Discharge to follow up

change_sf36 <- ORA %>% select(USUBJID, QUESTIONAIRESTYPE, PCS, MCS)

change_sf36 %>% 
	select(QUESTIONAIRESTYPE:MCS) %>% 
	tbl_summary(by = QUESTIONAIRESTYPE) %>% 
	add_p()

##effect of medicine to PCS and MCS

change_sf36 <- left_join(change_sf36, medicineeff, by = "USUBJID")

##Discharge
changesf36_dis <- change_sf36 %>% filter(QUESTIONAIRESTYPE == "Discharge")

relation <- rcorr(as.matrix(changesf36_dis[,-c(1,2,8)]))

dischargecor <- flattenCorrMatrix(relation$r, relation$P) %>% filter(p <= 0.05) ##choose the significant level 0.05

dischargecor
##Follow up

changesf36_fol <- change_sf36 %>% filter(QUESTIONAIRESTYPE == "Follow Up")

relation_fol <- rcorr(as.matrix(changesf36_fol[,-c(1,2,6:11)]))

folcor <- flattenCorrMatrix(relation_fol$r, relation_fol$P) %>% filter(p <= 0.05)

##There are significant improve in PCS and MCS score between 2 time points.
#Orthogonal rotation
#PF Physical Functioning - pf
#RP Role Physical - rh
#BP Bodily Pain - pa
#GH General Health - gh
#VT Vitality - ef
#SF Social Functioning - sf
#RE Role Emotional - eb
#MH Mental Health - rp

test1 <- aov(admission_discharge ~ PCS + MCS, data = changesf36_dis)

summary(test1)

test2 <- aov(admission_discharge ~ PCS + MCS, data = changesf36_fol)

summary(test2)

```


```{r HAIs}
icustay <- left_join(demograph, medicineeff, by = "USUBJID")

icumedicine <- rcorr(as.matrix(icustay[,c(3, 33:35)]))

flattenCorrMatrix(icumedicine$r, icumedicine$P) %>% filter(p < 0.05)

HAI <- select(IE_InterventionGrid, USUBJID, INTERVENTIONEVENT, YES) %>% 
	filter(INTERVENTIONEVENT == "HAIs")

HAItb <- select(timeonset, USUBJID, DAYSOFMECHVENT, geomean, newoutcome) %>% 
	left_join(HAI, by = "USUBJID") %>% 
	replace_na(list(
	YES = FALSE))

HAItb$YES <- as.character(HAItb$YES)

HAItb <- HAItb %>% mutate(YES = ifelse(YES == "TRUE", "HAIs", "Non-HAIs"))

HAItb %>% ungroup() %>% select(geomean, DAYSOFMECHVENT, YES, newoutcome) %>% tbl_summary(by = YES, label = list(
	DAYSOFMECHVENT ~ "Days of Mechanical vent",
	geomean ~ "Muscle change",
	newoutcome ~ "Outcome")) %>% add_p()

library("vcd")

assocstats(xtabs(~HAItb$YES + HAItb$geomean))

chisq.test(HAItb$YES, HAItb$geomean)
```

```{r EQ5D, eval = FALSE}

quol <- EQ5D %>% 
	select(USUBJID, TYPEOFQUESTIONAIRS, DISFOLLOWDTC, WALKING:WORRYSADNESS) %>%
	filter(USUBJID %in% demograph$USUBJID) %>% 
	filter(USUBJID %in% MUSCLE_MuscleUls$USUBJID) %>% 
	filter(if_any(c(WALKING:WORRYSADNESS), ~ !is.na(.)))

quol <- quol %>% 
	mutate(group = case_when(USUBJID %in% tetanus$USUBJID ~ "Tetanus",
													 USUBJID %in% cns$USUBJID ~ "CNS")) %>% 
	arrange(USUBJID, DISFOLLOWDTC) %>% 
	group_by(USUBJID) %>% 
	group_modify(~.x %>% mutate(TYPEOFQUESTIONAIRS = ifelse(row_number() == 1, "Discharge", "Follow Up"))) %>% 
	mutate(WORRYSADNESS = str_replace(WORRYSADNESS, "NotWorry", "1")) %>%
	mutate_at(c("WALKING", "SELFCARE", "BASICROUTINE", "PAIN", "WORRYSADNESS"), ~ as.numeric(.))

##For missing data will be replaced by the mean of 5 components of that individual
#table1(~ TYPEOFQUESTIONAIRS | group, data = quol)

##Missing data will be counted as mean of the range

quol <- ungroup(quol) %>% 
	mutate(across(c(WALKING:WORRYSADNESS), ~replace_na(.,round(mean(., na.rm = TRUE), 0))))
	
quol <- quol %>% mutate(eq5d = as.numeric(paste(WALKING, SELFCARE, BASICROUTINE, PAIN, WORRYSADNESS, sep = "")))

##convert score to Quality score range

score <- do.call(rbind, import_list("C:/Thaontp/Thao/Muscle/EQ-5D excel VN_ full.xlsx"))

colnames(score) <- c("eqscore", "quolscore")

score$quolscore <- parse_number(score$quolscore)

##look up from dataset to range score

quol <- left_join(quol, score, by = c("eq5d" = "eqscore")) %>% ungroup()

##Muscle data

#quoltb <- quol %>% select(TYPEOFQUESTIONAIRS, WALKING:WORRYSADNESS, quolscore, group) 

#tablescore <- describeBy(quoltb,
#					 group = list(quoltb$TYPEOFQUESTIONAIRS, quoltb$group),
#					 mat = TRUE,
#					 digits = 2) %>% 
#	select(-c(vars, item, trimmed, mad, skew, kurtosis, se))

#tablescore <- rownames_to_column(tablescore)

#tablescore <- tablescore %>% 
#	arrange(group2, group1) %>% 
#	group_by(group2)

#tablescore <- tablescore[!tablescore$rowname %in% c("TYPEOFQUESTIONAIRS*1", "TYPEOFQUESTIONAIRS*2", "TYPEOFQUESTIONAIRS*3", "TYPEOFQUESTIONAIRS*4", "group*1", "group*2", "group*3", "group*4"),]


#tablescore <- tablescore %>%
#	ungroup() %>% 
#	select(-c(group1, group2, n))

#colnames(tablescore) <- c("Characteristics", "Mean", "SD", "Median", "Min", "Max", "Range")

#tablescore$Characteristics <- gsub("\\d+", "", tablescore$Characteristics)

#tablescore$Characteristics <- str_replace_all(tablescore$Characteristics, 
#																							c("WALKING" = "Mobility", 
#																								"SELFCARE" = "Self-care",
#																								"BASICROUTINE" = "Usual activities",
#																								"PAIN" = "Pain/Discomfort", 
#																								"WORRYSADNESS" = "Anxiety/Depression", 
#																								"quolscore" = "QoL score"))

#Qol <- kbl(tablescore, caption = "EQ5D-5L and Quality of Life Scoring on Discharge and Followup") %>%
#	kable_styling("striped") %>%
#	group_rows("CNS", 1, 12) %>%
#	group_rows("TETANUS", 13, 24) %>% 
#  pack_rows("Discharge", 1, 6) %>%
#  pack_rows("Followup", 7, 12) %>%
#	pack_rows("Discharge", 13, 18) %>%
#  pack_rows("Followup", 19, 24) %>% 
#  footnote(general_title = "Note.", footnote_as_chunk = T, 
#           general = "N CNS Discharge = 28; N CNS Followup = 26; N Tetanus Discharge = 68; N Tetanus Followup = 61")


boxplot(quolscore ~ group + TYPEOFQUESTIONAIRS, quol, col = c("blue", "pink"), main = "Quality of life score improvement", names=c("CNS Discharge", "Tetanus Discharge", "CNS Follow Up", "Tetanus Follow Up"), xlab = "", ylab = "Quality of life score")

library(data.table)

total <- quol %>% 
	select(-quolscore) %>%
	as.data.table() %>% 
	melt(measure = c("WALKING", "SELFCARE", "BASICROUTINE", "PAIN", "WORRYSADNESS"),
			 value.name = "value")

library(scales)

improveeq5d <- total %>% mutate_at(c("value"), ~ as.character(.))

improveeq5d <- improveeq5d %>% rename(Score = value,
																			Component = variable)

#table1(~ Score |group + TYPEOFQUESTIONAIRS, data = improveeq5d)

##Total
totaltable <- improveeq5d %>% 
	group_by(TYPEOFQUESTIONAIRS, Component, Score) %>% 
	summarise(Freq = n())

totaltableComponent <- factor(totaltable$Component, levels = c("Mobility", "Self-care", "Usual activities", "Pain/Discomfort", "Anxiety/Depression"))

totaltable$Score <- str_replace_all(totaltable$Score, c("1" = "No problem",
																												"2" = "Slight",
																												"3" = "Moderate",
																												"4" = "Severe",
																												"5" = "Unable"))

totaltable$Score <- factor(totaltable$Score, levels = c("No problem","Slight","Moderate","Severe","Unable"))

graphtotal <- totaltable %>% 
	group_by(TYPEOFQUESTIONAIRS, Component) %>% 
	mutate(Percent = round(Freq/sum(Freq),2))

graphpercent <- graphtotal %>%
  ggplot(data = ., mapping = aes(x = Component, y = Percent, fill = Score)) +
  geom_col() +
  geom_text(mapping = aes(label = percent(Percent)),              # converting the values to percent
            size = 2,                                             # size of the font
            position = position_stack(vjust = 0.5)) +             # positioning in the middle
  scale_fill_brewer(palette = "Set3") +                           # coloring the plot
  facet_grid(.~TYPEOFQUESTIONAIRS) +
  labs(x = "EQ-5D-5L Components",                                              # labelling x axis
       y = "Percentage",                                        # labeling y axis
       title = "EQ-5D score improvement in all CNS and Tetanus patients",        # title
       fill = "EQ-5D-5L Score") +                               # legend
  scale_y_continuous(labels = scales::percent_format()) +
	theme_bw() +         # changing the y axis nber format
  theme(
    axis.text.x = element_text(angle = 45, vjust = 0.6, size = 8),                      # adjusting the position
    axis.title.x = element_text(face = "bold"),                   # face the x axit title/label
    axis.title.y = element_text(face = "bold"),                   # face the y axis title/label
    plot.title = element_text(hjust = 0.1),                       # positioning the plot title
    legend.title = element_text(face = "bold")                    # face the legend title
  )

graphpercent

eq5d_model <- left_join(medicineeff_mod, quol, by = "USUBJID") %>% 
	ungroup() %>% 
	select(changeharmonic, TOTALDOSEMIDAZOLAM:TYPEOFQUESTIONAIRS, quolscore) %>% 
	filter(!is.na(quolscore))

quol_dis <- eq5d_model %>% filter(TYPEOFQUESTIONAIRS == "Discharge")

quol_dis <- rcorr(as.matrix(quol_dis[,-5]))

quoltbdis <- flattenCorrMatrix(quol_dis$r, quol_dis$P) %>% filter(p <= 0.05)

quoltbdis

##choose the significant level 0.05

##Follow up

quol_fol <- eq5d_model %>% filter(TYPEOFQUESTIONAIRS == "Follow Up")

quol_fol <- rcorr(as.matrix(quol_fol[,-5]))

quoltbfol <- flattenCorrMatrix(quol_fol$r, quol_fol$P) %>% filter(p <= 0.05)

quoltbfol

```

```{r death analysis, eval= FALSE}

##outcome

deathanalysis <- timeonset %>% select(USUBJID, newoutcome, changeharmonic)

##HAIs

hosinfect <- IE_InterventionGrid %>% 
	select(USUBJID, INTERVENTIONEVENT, YES) %>% 
	filter(INTERVENTIONEVENT == "HAIs") %>% 
	filter(USUBJID %in% demograph$USUBJID)

##Admission haematology test

hemo <- ADM %>%
	select(USUBJID, HAEMOGLOBIN:WCC)%>% 
	filter(USUBJID %in% demograph$USUBJID)

##merging

deathanalysis <- deathanalysis %>% 
	left_join(hosinfect, by = "USUBJID") %>% 
	left_join(hemo, by = "USUBJID")

deathanalysis <- deathanalysis %>% mutate(YES = replace_na(YES, FALSE),
																					HAI = ifelse(YES == TRUE, 1L, 0L),
																					newoutcome = as.character(newoutcome))

deathanalysis %>% ungroup() %>% select(-c(USUBJID, INTERVENTIONEVENT)) %>% tbl_summary(by = newoutcome, missing = "no") %>% add_p()


#The improvement in Quality of life score shows no effect from muscle wasting has contribute in that. Let try at the time of discharge.

#Significant difference in PCS score between discharge and follow up

#The F-value column is the test statistic from the F test. This is the mean square of each independent variable divided by the mean square of the residuals. The larger the F value, the more likely it is that the variation caused by the independent variable is real and not due to chance.
#The Pr(>F) column is the p-value of the F-statistic. This shows how likely it is that the F-value calculated from the test would have occurred if the null hypothesis of no difference among group means were true.
```
